Beneficial arthropod habitat useage changes within-season: implications for pest control services in croplands

### 2020-10-01 manuscript/manuscript_outline.Rmd
Cleaned up figures

```{r siteMap, echo=FALSE, fig.cap='Location of pitfall traps during 2017, and classified cover f. Inset map shows study location within Alberta. Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field corners.'}  
  include_graphics('../figures/maps/PF2017Map.png',dpi=NA)
```

@@

```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location. Sites are represented by individual lines. Mean cover for each class is listed in each sub-figure heading.', fig.width=7, fig.height=7}  
coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
  mutate(cover=factor(cover,levels=unique(cover))) %>% 
  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
  facet_wrap(~cover,ncol=4)+theme_classic()+labs(y='Percent cover',x='Inner radius of annuli (m)')

@@

```{r PteMelLandscape, echo=FALSE, fig.cap='Landscape influence on _Pterostichus melanarius_ activity-density. Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pterostichus_melanarius_fixeff.png',dpi=NA)
```

@@

```{r ParDisLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa distincta_ activity-density. Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pardosa_distincta_fixeff.png',dpi=NA)
```

```{r ParMoeLandscape, echo=FALSE, fig.cap='Landscape influence on _Pardosa moesta_ activity-density. Lines and dots represent means, and bars and shaded regions represent 95% confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Pardosa_moesta_fixeff.png',dpi=NA)
```

@@

```{r OpilioLandscape, echo=FALSE, fig.cap='Landscape influence on _Phalangium opilio_ activity-density. Lines and dots represent means, and bars and shaded regions represent 95% confidence regions. Dashed line on panels b-f represents zero effect. Coloured regions represent early-, mid-, and late-season effects (red, green, blue)'}  
  include_graphics('../figures/Opiliones_fixeff.png',dpi=NA)
```

```{r rSquared, echo=FALSE}  
  r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>% 
  pivot_wider(names_from=model,values_from=r2comp) %>% 
  mutate(terms=case_when(terms=='trapLoc' ~ 'Trap Location', terms=='s(day)' ~ 'Day of Year',
                         terms=='s(E,N)' ~ 'Spatial Location', terms=='GrassWetland' ~ 'Grass/Wetland',
                         terms=='TreeShrub' ~ 'Trees/Shrubs', terms=='sigmaD' ~ 'Residual',
                         terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>% 
  kable(.,caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance attributable to each term.',
        col.names=c('Term','$\\emph{Pterostichus melanarius}$','$\\emph{Pardosa distincta}$','$\\emph{Pardosa moesta}$','$\\emph{Phalangium opilio}$'),
        digits=c(1,3,3,3,3),align='rllll',escape=FALSE) 
```

@@

```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models'}  
  include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png',dpi=NA)
```

```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pterostichus melanarius_ activity-density'}
  include_graphics('../figures/Pterostichus_melanarius_raneff.png',dpi=NA)
```

```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Pardosa distincta_ activity-density'}
  include_graphics('../figures/Pardosa_distincta_raneff.png',dpi=NA)
```

```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of \\emph{Pardosa moesta} activity-density'}
  include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)
```

```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='Temporal and spatial components of _Phalangium opilio_ activity-density'}
  include_graphics('../figures/Opiliones_raneff.png',dpi=NA)
```

>>>>

```{r siteMap, echo=FALSE, fig.cap='Location of pitfall traps during 2017, and classified cover f. Inset map shows study location within Alberta. Roadside traps were installed in road margins, while in-field traps were installed directly in canola fields or in adjacent wetland or grassy field corners.', out.width='100%'}  
  include_graphics('../figures/maps/PF2017Map.png',dpi=NA)
```

@@

```{r landscapeComp, echo=FALSE, fig.cap='Landscape composition in annuli surrounding each trap location. Sites are represented by individual lines. Mean cover for each class is listed in each sub-figure heading.', out.width='100%'}  
coverList %>% group_by(cover) %>% mutate(p=sum(prop)) %>% ungroup() %>% mutate(p=100*round(p/sum(unique(p)),4)) %>% 
  mutate(cover=paste0(as.character(cover),' (',p,'%)'),prop=prop*100) %>% 
  mutate(cover=factor(cover,levels=unique(cover))) %>% 
  ggplot(aes(dist,prop,group=site))+geom_line(alpha=0.2)+
  facet_wrap(~cover,ncol=4)+theme_classic()+labs(y='Percent cover',x='Inner radius of annuli (m)')

@@

<!-- Percent signs are escaped in LaTeX, but this causes havoc if used in fig.cap of chunk options (OK if used in internal captions, I think). Yihui uses "text references" instead. -->
(ref:PteMelCap) Landscape influence on _Pterostichus melanarius_ activity-density. Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue).

```{r PteMelLandscape, echo=FALSE, fig.cap='(ref:PteMelCap)', out.width='100%'}  
  include_graphics('../figures/Pterostichus_melanarius_fixeff.png',dpi=NA)
```

@@

(ref:ParDisCap) Landscape influence on _Pardosa distincta_ activity-density. Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue).

```{r ParDisLandscape, echo=FALSE, fig.cap='(ref:ParDisCap)', out.width='100%'}  
  include_graphics('../figures/Pardosa_distincta_fixeff.png',dpi=NA)
```

(ref:ParMoeCap) Landscape influence on _Pardosa moesta_ activity-density. Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue).

```{r ParMoeLandscape, echo=FALSE, fig.cap='(ref:ParMoeCap)', out.width='100%'}  
  include_graphics('../figures/Pardosa_moesta_fixeff.png',dpi=NA)
```

@@

(ref:OpilioCap) Landscape influence on _Phalangium opilio_ activity-density. Lines and dots represent means, and bars and shaded regions represent 95 % confidence intervals (1.96 x SE). Coloured regions represent early-, mid-, and late-season effects (red, green, blue).

```{r OpilioLandscape, echo=FALSE, fig.cap='(ref:OpilioCap)', out.width='100%'}  
  include_graphics('../figures/Opiliones_fixeff.png',dpi=NA)
```

```{r rSquared, echo=FALSE, out.width='100%'}  
  r2Nakagawa2 %>% select(model,terms,r2comp) %>% mutate(terms=as.character(terms),r2comp=r2comp*1) %>% 
  pivot_wider(names_from=model,values_from=r2comp) %>% 
  mutate(terms=case_when(terms=='trapLoc' ~ 'Trap Location', terms=='s(day)' ~ 'Day of Year',
                         terms=='s(E,N)' ~ 'Spatial Location', terms=='GrassWetland' ~ 'Grass/Wetland',
                         terms=='TreeShrub' ~ 'Trees/Shrubs', terms=='sigmaD' ~ 'Residual',
                         terms=='Urban' ~ 'Road margins', TRUE ~ terms)) %>% 
  kable(.,caption='R$^2_{GLMM}$ for model components, representing the proportion of total variance attributable to each term.',
        col.names=c('Term','$\\emph{Pterostichus melanarius}$','$\\emph{Pardosa distincta}$','$\\emph{Pardosa moesta}$','$\\emph{Phalangium opilio}$'),
        digits=c(1,3,3,3,3),align='rllll',escape=FALSE, table.attr = "style='width:30%;'") 
```

@@

```{r concurvity, echo=FALSE, fig.cap='Concurvity estimates for reduced cover classes used in models', out.width='100%'}  
  include_graphics('../figures/coverCorPlots/concurvityEstimate_reduced.png',dpi=NA)
```

(ref:PteMelSTCap) Temporal and spatial components of _Pterostichus melanarius_ activity-density (after accounting for landscape composition and trap location).

```{r PteMelSpatiotemporal, echo=FALSE, fig.cap='(ref:PteMelSTCap)', out.width='100%'}
  include_graphics('../figures/Pterostichus_melanarius_raneff.png',dpi=NA)
```

(ref:ParDisSTCap) Temporal and spatial components of _Pardosa distincta_ activity-density (after accounting for landscape composition and trap location).

```{r ParDisSpatiotemporal, echo=FALSE, fig.cap='(ref:ParDisSTCap)', out.width='100%'}
  include_graphics('../figures/Pardosa_distincta_raneff.png',dpi=NA)
```

(ref:ParMoeSTCap) Temporal and spatial components of _Pardosa moesta_ activity-density (after accounting for landscape composition and trap location).

```{r ParMoeSpatiotemporal, echo=FALSE, fig.cap='', out.width='100%'}
  include_graphics('../figures/Pardosa_moesta_raneff.png',dpi=NA)
```

(ref:OpilioSTCap) Temporal and spatial components of _Phalangium opilio_ activity-density (after accounting for landscape composition and trap location).

```{r OpilioSpatiotemporal, echo=FALSE, fig.cap='(ref:OpilioSTCap)', out.width='100%'}
  include_graphics('../figures/Opiliones_raneff.png',dpi=NA)
```
